\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }

\begin{document}

\title{Week 13 Writing Activity: Citations in Essays and Articles}
\author{Prof. Jordan C. Hanson (INTD100)}

\maketitle

\section{Unpacking Citations}

For each of the sentences below, list the (a) The article title, (b) the main authors, (c) the title of the publishing journal, (d) the volume number of the journal, and (e) the year of publication.

\begin{enumerate}
\item One method for searching for UHE neutrino signals involves matching observed RF waveforms with analytical predictions of the Askaryan effect \cite{HH}.
\begin{itemize}
\item (a)
\item (b)
\item (c)
\item (d)
\item (e)
\end{itemize}
\item The authors of \cite{horiz} have shown that RF signals can propagate horizontally in natural ice environments, even when the index of refraction is not constant.
\begin{itemize}
\item (a)
\item (b)
\item (c)
\item (d)
\item (e)
\end{itemize}
\item Figure 4 of \cite{H} contains computational electromagnetic (CEM) results that demonstrate the beam angle of an RF phased array is proportional to the phase shift per radiating element.
\begin{itemize}
\item (a)
\item (b)
\item (c)
\item (d)
\item (e)
\end{itemize}
\item \textbf{DOI}: the DOI, or \textit{digital object identifier}, is used as a hyperlink to direct the reader to the original online publication.  In articles, the link can be embedded like: \href{https://doi.org/10.1103/PhysRevD.105.123019}{analytic Askaryan model}.
\end{enumerate}

\begin{thebibliography}{10}
\bibitem{HH} Hanson, J.C., and Hartig, R., ``Complex Analysis of Askaryan Radiation: A fully analytic model in the time domain,'' \emph{Physical Review D}, vol. 105, 123019, June 2022. \url{https://doi.org/10.1103/PhysRevD.105.123019}.
\bibitem{H} Hanson, J.C., ``Broadband RF Phased Array Design with MEEP: Comparisons to Array Theory in Two and Three Dimensions,'' \emph{Electronics Journal}, vol. 10, n. 4, p. 415, February 2021. \url{https://doi.org/10.3390/electronics10040415}.
\bibitem{horiz} Barwick, S.W. \textit{et al}, ``Observation of classically `forbidden' electromagnetic wave propagation and implications for neutrino detection,'' \emph{Journal of Cosmology and Astroparticle Physics}, vol. 07, p. 55, July 2018. \url{https://doi.org/10.1088/1475-7516/2018/07/055}.
\end{thebibliography}

\end{document}
