\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}

\begin{document}

\title{Week 2 Writing Activity: \textit{Concise Writing and Misconceptions about Science}}
\author{Prof. Jordan C. Hanson (INTD100)}

\maketitle

\section{Chapter 3 of \textit{The Scientific Attitude}: First Long Writing Assignment}

\begin{enumerate}
\item Consider the following stories from Chapter 3 of \textit{The Scientific Attitude}:
\begin{itemize}
\item The story of Dr. Ignaz Semmelweis, the doctor working in the maternity wards of a Vienna hospital, who discovered a way to decrease maternal deaths after giving birth.
\item The story of Profs. B. Stanley Pons and Martin Fleischmann, who falsely claimed to discover cold fusion, in what would have been a breakthrough for cheap and clean energy production.
\end{itemize}
And consider these additional stories
\begin{itemize}
\item The story of Dr. Andrew Wakefield and his colleagues, who falsely claimed to discover a link between the MMR vaccine and autism in children.
\item The story of John Couch Adams and Urbain Le Vernier, who discovered the planet Neptune in 1846 (independently).
\end{itemize}
\item First, write a 1500-word essay covering the scientific history of one of the four stories above.  Your work should include:
\begin{itemize}
\item The historical context of the discovery or false discovery
\item How the \textit{Scientific Attitude} was applied or not applied correclty
\item Specific scientific details explaining the findings for the reader
\end{itemize}
\end{enumerate}

\section{Concise Writing I: Trimming an Essay}

\begin{enumerate}
\item Second, reduce the length of your essay \textit{after completing it,} by using the concise writing techniques we have been practicing.  The final result should be no more than 1000 words.  Turn in both copies by \textbf{Saturday, September 17th}, via the submission link on Moodle.
\item Remember to take advantage of our writing tutor, Jasmine Arada, in CAAS on Thursdays from 8:50 to 10:50 for help.
\end{enumerate}

\end{document}
