\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}
\usepackage{hyperref}

\begin{document}

\title{Week 12 Writing Activity: Writing Mechanics in Essays and Articles and Chapter 8 of \textit{The Scientific Attitude}}
\author{Prof. Jordan C. Hanson (INTD100)}

\maketitle

\section{Links for Today}
\textbf{Summary of 10 Court Cases Involving Science Education and Biological Evolution} \\ \\
\url{https://ncse.ngo/ten-major-court-cases-about-evolution-and-creationism} \\ \\
\url{https://en.wikipedia.org/wiki/Intelligent_design}

\section{Pseudo-Science, Evolution, and Creationism}

\begin{enumerate}
\item Please open the link above, from the National Center for Science Education (NCSE) to find a list of court cases mentioned in Chapter 8 of \textit{The Scientific Attitude}.  In these cases, which reached varying levels of the State and Federal judiciary, the biological theory of evolution is challenged with \textit{creationism} or \textit{intelligent design} (ID).  (a) Using the language of the scientific attitude, write a few sentences explaining why the proponents of creationism lost each of the ten cases.  What part of the process of science education is in question in each case? (b) \textit{Design your own court case}, in which you seek to challenge the biological theory of evolution.  What part of the science education process would you choose to attack, and how would you argue that your alternative theory explains the world in a better way than evolution? \\ \vspace{3cm}
\item In Chapter 8, the theory of \textit{intelligent design} (ID) is described as an offshoot of creation science.  Intelligent design has two main precepts: \textit{irreducable complexity} and \textit{specified complexity}.  (a) Visit the second link above, and record here in your own words the definition of these two terms.  (b) Here is a classic thought experiment that generates discussion between ID and evolution: ``Suppose you are walking in a field, in the middle of the wilderness.  You encounter a pocketwatch, with hands for hours, minutes, and seconds.  Do you conclude that it evolved through natural processes, or is it there because someone intelligent designed it, built it, and placed it there?''  In light of what we know about evolution, and ID, and the scientific attitude, answer the thought experiment in your own words.
\end{enumerate} 

\end{document}
