\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}
\usepackage{hyperref}

\begin{document}

\title{Week 10 Writing Activity: Writing Mechanics in Essays and Articles}
\author{Prof. Jordan C. Hanson (INTD100)}

\maketitle

\section{Splitting the Sentence}

A common mistake in essays and articles is to create sentences that contain too many ideas.  Below are examples of sentences that need to be split into several sentences, with one idea per sentences.  Split each sentence into \textit{at least two} sentences.

\begin{enumerate}
\item One example of when I had to be a leader was when the captain of my rugby team in college resigned so I had to step up and bring the team together. \\ \vspace{1cm}
\item Once I become a computer programmer, I would like to give back to my community by creating an application that helps middle school students learn chemistry because I believe this will give them a higher chance of success in their professional lives. \\ \vspace{1cm}
\item I have drawn inspiration for leaderhip from my family, which helped me when I was called to stand up for what was right when I noticed my friend was being bullied at school. \\ \vspace{1cm}
\item My friends and I were hiking in the mountains and we got lost, so I decided to take charge and orient the map with my compass so that we could find our way home which required me to control my emotions and thoughts. \\ \vspace{1cm}
\item I was asked to lead a recycling group in school, so I created a plan and delegated responsibilities and ensured that that food waste was composted and aluminum and plastic were sorted into proper bins.  \\ \vspace{1cm}
\end{enumerate}

\section{Creating an Abstract}

\textbf{Imagine using a pendelum to measure the gravitational acceleration of the Earth.}  The purpose of an abstract is to contextualize and describe your work in a concise and easily-understood manner.  An abstract is a paragraph that appears before the main body of writing.  \textbf{Professor}: lead a discussion on the organization of an abstract.

\end{document}
